---
title: "Langebaan2018Markdown"
author: "Shani Fourie"
date: "12/04/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

#### Introduction

The aim of the study was to assess how disturbance (bait collecting and trampling) influence trophic niches of sandprawns.The study was done in Langebaan lagoon in Zone A. Zone A was further divided into four sections, A1, A2, B and C. To access the raw data used in this document click [here.](https://github.com/ShaniFourie/TidyData/blob/main/ShaniRaw.xlsx)



```{r echo=FALSE}
library(readxl)
library(tidyverse)

```

Within the 4 subsections of Zone A five variables were measured for each of the four materials (Sandprawn, plants, phytoplankton and MPB, and the sediment). These variables are as follows: delta carbon 13, delta nitrogen 15, the % nitrogen present, the % carbon present, and the carbon to nitrogen ratio.

A table representing the collected data for the Sandprawn


Reading in the different sheets from excel
```{r}
Sandprawn <- read_excel("ShaniRaw.xlsx",  sheet = "Sandprawn")


plants <- read_excel("ShaniRaw.xlsx", sheet = "Plants")


phyto <- read_excel("ShaniRaw.xlsx", sheet = "PHY and MBO")


sediment <- read_excel("ShaniRaw.xlsx", sheet = "Sediment")

```


Changing sediments' "Zone" to "Site"
```{r}
SedimentSite=read_excel("ShaniRaw.xlsx", sheet = "Sediment")%>%
knitr::kable(col.names = c("Material", "Site", "d13C",  "d15N",  "`N%`", "`C%`"))

```

```{r}
SedimentSite
```



Displaying the data in tabular format for the four different materials:
```{r}
Sandprawn
plants
phyto
sediment
```

Selecting specific columns from the Sandprawn table

```{r }
SandprawnSelected=read_xlsx("ShaniRaw.xlsx", sheet= "Sandprawn") %>% 
  select(Material,Site,d13C,d15N,`N%`,`C%`,`C:N`)

SandprawnSelected

```


The characters are set as factors and unclassed
```{r echo=FALSE,message=FALSE}
Sandprawn$Sex = as.factor(Sandprawn$Sex)
unclass(Sandprawn$Sex)

Sandprawn$Site = as.factor(Sandprawn$Site)
unclass(Sandprawn$Site)

plants$Site = as.factor(plants$Site)
unclass(plants$Site)

phyto$Site = as.factor(phyto$Site)
unclass(phyto$Site)

sediment$Zone = as.factor(sediment$Zone)
unclass(sediment$Zone)
```



##**The data is then tidied to pivot longer**

Sandprawn table pivot to long format:

```{r}
read_xlsx("ShaniRaw.xlsx", sheet= "Sandprawn") %>% 
  select(Material,Site,d13C,d15N,`N%`,`C%`) %>%
  pivot_longer(cols = c("d13C", "d15N", "N%", "C%"),
               names_to = "variable", values_to = "value") 
```

Sediment table pivot to long format
```{r}
sediment%>%
  pivot_longer(cols = c("d13C", "d15N", "N%", "C%"),
               names_to = "variable", values_to = "value")
```

Plant table pivot to long format:
```{r}
plants %>%
  pivot_longer(cols = c("d13C", "d15N", "N%", "C%"),
               names_to = "variable", values_to = "value") 
```

Phytoplankton table pivot to long format:
```{r}
phyto %>%
  pivot_longer(cols = c("d13C", "d15N", "N%", "C%"),
               names_to = "variable", values_to = "value") 
```




```{r echo=FALSE, message=FALSE}
 library(ggplot2)
```

```{r}

```

## Plots

The delta 13 carbon values for Sandprawn, plants, phytoplankton and MPB, and sediment, collected within the four sites:

```{r }



```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
