---
title: "Langebaan2018Markdown"
author: "Shani Fourie"
date: "12/04/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

####Header4 Introduction

The aim of the study was to assess how disturbance (bait collecting and trampling) influence trophic niches of sandprawns.The study was done in Langebaan lagoon in Zone A. Zone A was further divided into four sections, A1, A2, B and C. To access the raw data used in this document click [here.](https://github.com/ShaniFourie/TidyData/blob/main/ShaniRaw.xlsx)

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
library(readxl)
library(tidyverse)

SandprawnSelected=read_xlsx("ShaniRaw.xlsx", sheet= "Sandprawn") %>% 
  select(Material,Site,d13C,d15N,`N%`,`C%`,`C:N`)

SandprawnSelected
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
